Analysis of the inference of ratings and rankings on Higher Order Networks with complex topologies

### 2025-09-08 draft/draft.tex
progress

\section{
Theory
\label{sec:theory}
}

\subsection{HodgeRank for inference of team's ratings and rankings}

%Consider a set of $N=n+1$ teams labeled by $\{0,1,...,n\}$ to be rated and ranked.
%For this aim, assume that some set of pairwise comparison scores $\psi_{ij}=-\psi_{ji}$ is provided for each pair $ij$ of different teams $i$ and $j$.
%Informally, the score $\psi_{ij}$ should be positive if the comparison indicates that team $i$ should preferably be rated higher than team $j$ and the opposite otherwise.
%
%One way to infer rating scores somehow consistent with the pairwise comparisons scores $\phi_{ij}$, consist in finding ratings $w_i$ for $i=0,1,..,n$ that minimize the sum of squared differences
%$$
%\sum_{ij:i<j} |\psi_{ij}-(w_i-w_j)|^2.
%$$
%This is a well defined mathematical problem that can be conveniently reformulated in the language of cochains over simplicial complexes, conceiving a method for the inference of ratings and rankings that is named  HodgeRank~\cite{jiang2011statistical,
%perotti2025analysis}.

Consider a set of $N=n+1$ teams labeled $\{0,1,\dots,n\}$ to be rated and ranked.
Suppose that for each distinct pair of teams $i$ and $j$, a pairwise comparison score $f_{ij}=-f_{ji}$ is given.
Informally, $f_{ij}>0$ suggests that team $i$ should be rated higher than team $j$, while $f_{ij}<0$ suggests the opposite.

A natural approach to inferring rating scores consistent with the pairwise comparisons is to assign ratings $f_i$ (for $i=0,1,\dots,n$) that minimize the sum of squared discrepancies
$$
\sum_{i<j} \bigl(f_{ij}-(f_i-f_j)\bigr)^2.
$$
This yields a well-posed optimization problem that admits an elegant reformulation in the language of cochains over simplicial complexes.
The resulting framework for the inference of ratings and rankings is known as {\em HodgeRank}~\cite{jiang2011statistical, perotti2025analysis}.

%To define HodgeRank, it is convenient to introduce a simplicial complex composed of a 0-simplex $i$ for each team, a 1-simplex $ij$ for each pairwise comparison $\psi_{ij}$ between teams and a 2-simplex $ijk$ for each existing triple $(ij,jk,ki)$ in the set of 1-simplices.
%Recall here that $ij$ and $ji$ are both labels of the same simplex, as well as any permutation of $ijk$ is also a label of the same 2-simplex.

\subsection{Discrete calculus on simplicial complexes}

To define HodgeRank, an abstract simplicial complex has to be defined.
For this, let the vertex set be $V=\{0,1,\dots,n\}$, representing the teams, and let the edge set $E$ consist of the unordered pairs $\{i,j\}$ for which a pairwise comparison score $\psi_{ij}$ is available.
Then, the associated abstract simplicial complex is
$$
K = K_0 \cup K_1 \cup K_2,
$$
where
\begin{eqnarray}
K_0 &=& \{\{i\} : i \in V\}, \notag \\  
K_1 &=& \{\{i,j\} : \{i,j\} \in E\}, \notag \\
K_2 &=& \{\{i,j,k\} : \{i,j\},\{j,k\},\{k,i\} \in E\} \notag
\end{eqnarray}
are the sets of 0, 1 and 2 simplices, respectively.
Thus, each team corresponds to a 0-simplex, each comparison to a 1-simplex, and each closed triple of comparisons to a 2-simplex.
By convention, $\{i,j\}=\{j,i\}$ denotes the same 1-simplex, and any permutation of $\{i,j,k\}$ denotes the same 2-simplex.

Next, the simplicial complex is equipped with a vector space $C$ of vectors called chains, whose canonical basis is denoted by $\{e_s:s\in K\}$.

The vector space of chains $C$ is equipped with the trivial inner product
$$
e_r.e_s = \delta_{rs}
$$
for each pair $r,s \in K$.
Using Einstein's implicit summation convention, an arbitrary chain $c$ in $C$ can be linearly decomposed in the canonical basis as $c=c^se_s$ where the $c^s$ are coefficients in $\RR$.
The vector space of chains admits the following decomposition in direct sums
$$
C = C_0\oplus C_1\oplus C_2
$$
where $C_k$ is the subspace of $C$ spanned by the basis of $k$-chains, i.e. by $\{e_s:s\in K_k\}$.

The covectors $f$ in the dual space $C^*$ of $C$ are called cochains.
The dual basis is denoted by $\{e^s:s\in K\}$ and satisfies
$$
e^r(e_s) = \delta^r{}_s
$$
for each $s,r\in K$.
An arbitrary cochain $f$ in $C^*$ can be linearly decomposed in the dual basis as $f=f_se^s$ where the $f_s$ are coefficients in $\RR$.
The vector space of cochains admits the following decomposition in direct sums
$$
C^* = C_0^*\oplus C_1^*\oplus C_2^*
$$
where $C_k^*$ is the subspace of $C^*$ spanned by the dual basis of $k$-cochains, i.e. by $\{e^s:s\in K_k\}$.

Riesz's theorem establishes that for any cochain $f\in C^*$, there is an unique chain in $C$ denoted by $f^{\flat}$ such that $f(q) = f^{\flat}.c$ for any chain $c\in C$.
This results, induces an inner product on on $C^*$ given by
$$
f.g = f^{\flat}.g^{\flat}
$$
for any pair of cochains $f,g\in C^*$.
The map $C^*\ni f\to f^{\flat}\in C$ is an isomorphism, whose inverse is denoted by $C\ni c\to c^{\sharp}\in C^*$.

A notion of orientation is imposed to the vector space of chains, by requering that
$$
e_s
=
e_{i_0...i_k}
=
(-1)^p
e_{j_0...j_k}
$$
for each simplex $s=\{i_0,...,i_k\}$ of $K$
when $0\leq i_0<i_1<...<i_k\leq n$ and $p$ is the parity of the permutation taking the sequence $i_0...i_k$ into the sequence $j_0...j_k$.

Thanks to the notion of orientation, a boundary linear operator $\partial:C\to C$ can be defined by its action on the vectors of the canonical basis, i.e. by
$$
\partial e_{i_0...i_k}
=
\sum_{j=0}^k
(-1)^j
e_{i_0...i_{j-1}i_{j+1}...i_k}
$$
for any $e_{i_0...i_k}\in C$.
Note that $\partial(C_k) \subseteq C_{k-1}$, where $C_{-1}=\{0\}$ denotes the trivial subspace of $C$ of dimension 0.
This induces the following direct sum decomposition
$$
\partial = \partial_0 \oplus \partial_1 \oplus \partial_2
$$
where $\partial_k(C)=\partial(C_k)\subseteq C_{k-1}$ and, in particular, $\partial_0=0$.

Since the application of any cochain $f$ to any chain $c$ is a bilinear form, the coboundary linear operator $d:C^*\to C^*$ is univocally defined by the relation
$$
df(c) = f(\partial c)
$$
for any $f\in C^*$ and $c\in C$.
Note, $d(C_k^*)\subset C_{k+1}^*$ where $C_3^*=\{0\}$ denotes the trivial subspace of $C^*$ of dimension 0.
As before, this induces the following direct sum decomposition
$$
d = d_0 \oplus d_1 \oplus d_2
$$
where $d_k(C^*)=d(C_k^*)\subseteq C_{k+1}^*$ and, in particular, $d_2=0$.

Since the inner products on $C$ and $C^*$ are also bilinear forms, then the dual boundary $\partial^*:C\to C$ and the dual coboundary $d^*:C^*\to C^*$ linear operators can be univocally defined by
$$
\partial^*c.q
=
c.\partial q
$$
and
$$
d^*f.g
=
f.d g,
$$
for any chains $c,q\in C$ and any cochains $f,g\in C^*$, respectively.
Note, that $\partial^*(C_{k-1})\subseteq C_k$ and $d^*(C_{k+1}^*)\subseteq C_k^*$, indicing the follow direct sum decompositions
$$
\partial^* = \partial_0^* \oplus \partial_1^* \oplus \partial_2^*
$$
and
$$
d^* = d_0^* \oplus d_1^* \oplus d_2^*
$$
where $\partial_k^*(C)=\partial^*(C_{k-1})\subseteq C_k$ and $d_k^*(C^*)=d(C_{k+1}^*)\subseteq C_k^*$.

The boundary and coboundary operators and their duals can be used to define the so called Hodge Laplacians
$$
\mathcal{L} = (\partial + \partial^*)^2 = \partial \partial^* + \partial^* \partial
: C\to C
$$
and
$$
L = (d+d^*)^2 = dd^* + d^*d : C^*\to C^*
$$
where the fact that $\partial^2 = (\partial^*)^2 = 0$ and $d^2=(d^*)^2=0$ is used.
The first identity $\partial^2=0$ is implied by the alternating properties of the definition of $\partial$, from where the other identities follow.
These Hodge Laplacians satisfy the following decomposition in direct sums
$$
\mathcal{L}
=
\mathcal{L}_0
\oplus
\mathcal{L}_1
\oplus
\mathcal{L}_2
$$
and
$$
L = L_0 \oplus L_1 \oplus L_2,
$$
where in turn
$$
\mathcal{L}_k = \mathcal{L}_k^{\downarrow} \oplus \mathcal{L}_k^{\uparrow} : C_k\to C_k,
$$
$$
L_k = L_k^{\downarrow} \oplus L_k^{\uparrow} : C_k^* \to C_k^*,
$$
$$
\mathcal{L}_k^{\downarrow} = \partial_k^*\partial_k : C_k \to C_{k-1} \to C_k,
$$
$$
\mathcal{L}_k^{\uparrow} = \partial_{k+1}\partial_{k+1}^* : C_k \to C_{k+1} \to C_k,
$$
$$
L_k^{\uparrow} = d_k^*d_k : C_k^* \to C_{k+1}^* \to C_k^*,
$$
and
$$
L_k^{\downarrow} = d_{k-1}d_{k-1}^* : C_k^* \to C_{k-1}^* \to C_k^*.
$$

Any $k$-cochain $f$ admits the so called Hodge decomposition
$$
f = g\oplus h\oplus s
$$
where the direct sum components $g\in \rng d_{k-1}$, $h\in \krn L_k$ and $s\in \rng d_k^*$ are unique and are called the gradient, the harmonic and the solenoid components, respectively.
As a consequence, there exists non-unique cochains $w\in C_{k-1}^*$ and $u\in C_{k+1}^*$ such that $g=d_{k-1}w$ and $s=d_k^*u$, that can be found solving for
\begin{eqnarray}
d_kf 
&=&
d_k(g+h+s)
\notag
\\
&=&
d_k s
\notag
\\
&=&
d_k d_k^* u
\notag
\\
&=&
L_{k+1}^{\downarrow} u
\notag
\end{eqnarray}
and
\begin{eqnarray}
d_{k-1}^* f 
&=&
d_{k-1}^*(g+h+s)
\notag
\\
&=&
d_{k-1}^* g
\notag
\\
&=&
d_{k-1}^*d_{k-1} w
\notag
\\
&=&
L_{k-1}^{\uparrow} w,
\notag
\end{eqnarray}
while the harmonic component can be found from $h=f-g-s$.

\subsection{Discrete calculus reformulation of the infererence of ratings}

@@

@@

The dataset covers five soccer leagues: England, France, Germany, Italy, and Spain.
Each league consists of $N=20$ teams, except for Germany, which has $N=18$.
Every pair of teams $i,j$ plays two matches: one with $i$ as the home team and $j$ as the away team, and in the other match it is the other way around.
The teams are indexed or ranked according to their position in that year’s final standings.
The standings is characterized by some tournament points $\pi_i$ for each team $i$ in each league.
Therefore, the condition $i<j$ holds if and only if $\pi_i>\pi_j$ for any two teams $i$ and $j$ in a given league.

For each pair of teams $i$ and $j$ in a given league, several pairwise metrics $m_{ij}\in \mathbb{R}$ are provided.
Each metric takes a positive value if it presumably favors team $i$ over team $j$, and a negative value otherwise.
The different types of empirically determined metrics being considered are:
\begin{enumerate}
\item {\bf crossings:}
\item {\bf counterattacks:}
\item {\bf pressure loss:}
\item {\bf build-up time:}
\item {\bf direct play:}
\item {\bf pressure points:}
\item {\bf shots:}
\item {\bf flow rate:}
\item {\bf maintenance time:}
\item {\bf middle-zone time:} bla bla.
\end{enumerate}
Namely, $m_{ij}$ corresponds to $i$ being the home team and $j$ being the away team.
Additionally, metric-styles derived from the Singular Value Decomposition of previous metrics are also considered~\cite{chacoma2025data}.
Notice, $m_{ij}$ is generally independent of the metric $m_{ji}$ since they belong to different matches between $i$ and $j$.
As a consequence, $m_{ij}+m_{ji}$ is generally different from zero and is the net contribution between teams $i$ and $j$.

@@

With each metric, the coefficients
$$
f_{ij}
=
\frac{1}{2}(m_{ij}+m_{ji})
$$
are defined for each $i$ and $j$ in $\{0,1,...,n\}$ such that $i<j$ and where $N=n+1$ is the number of teams in the corresponding league.
Moreover, in order to test the inference method, two types of ground-truth coefficients are also defined.
Namely, the rank-based coefficients $f_{ij}=i-j$ and the tournament points based coefficients $f_{ij}=\pi_j-\pi_i$.
These coefficients correspond to a fully connected network or graph with $N$ nodes since, as already mentioned, all pairs of teams play two matches against each other in each league.
Next, each fully connected graphs is promoted to a simplicial complex composed of 0-simplices labeled by $i$, 1-simplices labeled by $ij$ with $i<j$ and 2-simplices labeled by $ijk$ with $i<j<k$.
Finally, the coefficients $f_{ij}$ are promoted to be the components of a 1-cochain  $f$, where the anti-symmetric relation $f_{ji}=-f_{ij}$ must hold by definition.

>>>>

\section{Theory}
\label{sec:theory}

\subsection{Least-squares inference of team ratings and rankings}

Consider a set of $N=n+1$ teams labeled $\{0,1,\dots,n\}$.
For each distinct pair of teams $i$ and $j$, assume that a pairwise comparison score $f_{ij}=-f_{ji}$ is available.
Intuitively, $f_{ij}>0$ indicates that team $i$ should be rated higher than team $j$, whereas $f_{ij}<0$ suggests the opposite.

A natural approach to inferring ratings consistent with these comparisons is to assign scores $w_i$ (for $i=0,1,\dots,n$) that minimize the sum of squared discrepancies:
\begin{equation}
\label{eq:1}
\sum_{i<j} \bigl(f_{ij}-(w_i-w_j)\bigr)^2.
\end{equation}
Once the team ratings $w_0,w_1,\dots,w_n$ have been inferred, the ranking $r_0,r_1,\dots,r_n$ is obtained by requiring that $r_i<r_j$ whenever $w_i>w_j$.
This setup leads to a well-posed optimization problem that admits an elegant reformulation in terms of cochains over simplicial complexes.
The resulting framework for rating and ranking inference is known as \emph{HodgeRank}~\cite{jiang2011statistical, perotti2025analysis}.

\subsection{Discrete exterior calculus on simplicial complexes}

To review the HodgeRank method, we summarize the basic elements of discrete exterior calculus on simplicial complexes.  
Let $V=\{0,1,\dots,n\}$ denote a set of vertices.  
A simplicial complex is a collection
\[
K = K_0 \cup K_1 \cup \dots \cup K_n
\]
where
\[
K_k \subseteq \bigl\{\{i_0,\dots,i_k\} : 0\leq i_0<\dots<i_k\leq n,\ i_j\in V\bigr\},
\]
of $k$-simplices, i.e. unordered subsets $\{i_0,\dots,i_k\}$ of the vertex set satisfying the closure condition: if $s\in K$ and $r\subset s$ with $r\neq \emptyset$, then $r\in K$.

The set $K$ of simplices is associated with a vector space $C$ of vectors called chains, whose canonical basis is denoted by $\{e_s:s\in K\}$.
We equip $C$ with the trivial inner product
\[
e_r \cdot e_s = \delta_{rs}, \qquad r,s \in K.
\]
Using Einstein summation convention, any chain $c\in C$ can be written as $c=c^se_s$ with coefficients $c^s\in \mathbb{R}$.
The chain space decomposes into
\[
C = C_0 \oplus C_1 \oplus C_2,
\]
where $C_k$ is the subspace spanned by $\{e_s:s\in K_k\}$.

Dually, the space of cochains $C^*$ is spanned by $\{e^s:s\in K\}$, where $e^r(e_s)=\delta^r{}_s$.
Any $f\in C^*$ decomposes as $f=f_se^s$ with coefficients $f_s\in \mathbb{R}$, and
\[
C^* = C_0^* \oplus C_1^* \oplus C_2^*.
\]

By Riesz’s theorem, every cochain $f\in C^*$ corresponds uniquely to a chain $f^\flat \in C$ such that $f(c) = f^\flat \cdot c$ for all $c\in C$.
This induces an inner product on $C^*$:
\[
f\cdot g = f^\flat \cdot g^\flat.
\]
The map $f\mapsto f^\flat$ is an isomorphism, with inverse denoted by $c\mapsto c^\sharp$.

\medskip

\noindent\textbf{Orientation and boundary.}  
An orientation is imposed on chains by requiring
\[
e_s = e_{i_0\dots i_k} = (-1)^p e_{j_0\dots j_k},
\]
for each simplex $s=\{i_0,\dots,i_k\}\in K$, where $0\leq i_0<\dots<i_k\leq n$ and $p$ is the parity of the permutation taking $(i_0,\dots,i_k)$ into $(j_0,\dots,j_k)$.

The boundary operator $\partial:C\to C$ is defined on basis elements as
\[
\partial e_{i_0\dots i_k}
=
\sum_{j=0}^k (-1)^j e_{i_0\dots i_{j-1}i_{j+1}\dots i_k}.
\]
Thus $\partial(C_k)\subseteq C_{k-1}$, with $C_{-1}=\{0\}$.
This yields the decomposition
\[
\partial = \partial_0 \oplus \partial_1 \oplus \partial_2,
\]
where $\partial_k(C_k)\subseteq C_{k-1}$ and $\partial_0=0$.

\medskip

\noindent\textbf{Coboundary.}  
The coboundary operator $d:C^*\to C^*$ is defined by
\[
df(c) = f(\partial c),
\]
for all $f\in C^*$ and $c\in C$.
Thus $d(C_k^*) \subseteq C_{k+1}^*$, with $C_3^*=\{0\}$, and
\[
d = d_0 \oplus d_1 \oplus d_2, \qquad d_2=0.
\]

\medskip

\noindent\textbf{Adjoint operators.}  
Since the inner products on $C$ and $C^*$ are bilinear, the adjoint operators $\partial^*:C\to C$ and $d^*:C^*\to C^*$ are defined by
\[
\partial^*c \cdot q = c\cdot \partial q, 
\qquad 
d^*f \cdot g = f\cdot dg,
\]
for all $c,q\in C$ and $f,g\in C^*$.
These satisfy
\[
\partial^* = \partial_0^* \oplus \partial_1^* \oplus \partial_2^*, 
\qquad 
d^* = d_0^* \oplus d_1^* \oplus d_2^*.
\]

\medskip

\noindent\textbf{Hodge Laplacians.}  
The boundary and coboundary operators define the Hodge Laplacians
\[
\mathcal{L} = (\partial+\partial^*)^2 = \partial\partial^* + \partial^*\partial : C\to C,
\]
\[
L = (d+d^*)^2 = dd^* + d^*d : C^*\to C^*,
\]
where $\partial^2=(\partial^*)^2=d^2=(d^*)^2=0$.
These decompose as
\[
\mathcal{L} = \mathcal{L}_0 \oplus \mathcal{L}_1 \oplus \mathcal{L}_2, 
\qquad 
L = L_0 \oplus L_1 \oplus L_2,
\]
with
\[
\mathcal{L}_k = \mathcal{L}_k^{\downarrow}\oplus \mathcal{L}_k^{\uparrow}, 
\qquad 
L_k = L_k^{\downarrow}\oplus L_k^{\uparrow},
\]
\[
\mathcal{L}_k^{\downarrow} = \partial_k^*\partial_k, \quad 
\mathcal{L}_k^{\uparrow} = \partial_{k+1}\partial_{k+1}^*, 
\]
\[
L_k^{\uparrow} = d_k^*d_k, \quad 
L_k^{\downarrow} = d_{k-1}d_{k-1}^*.
\]

\medskip

\noindent\textbf{Hodge decomposition.}  
Every $k$-cochain $f$ admits the Hodge decomposition
\[
f = g \oplus h \oplus s,
\]
where $g\in \operatorname{im} d_{k-1}$ (gradient), $h\in \ker L_k$ (harmonic), and $s\in \operatorname{im} d_k^*$ (solenoidal).
Equivalently, there exist $w\in C_{k-1}^*$ and $u\in C_{k+1}^*$ such that
\[
g = d_{k-1}w, \qquad s = d_k^* u,
\]
with $w$ and $u$ determined by
\begin{align}
\label{eq:2}
d_k f &= L_{k+1}^{\downarrow} u, \\
\label{eq:3}
d_{k-1}^* f &= L_{k-1}^{\uparrow} w,
\end{align}
while $h=f-g-s$.

\subsection{HodgeRank}

Expression~\eqref{eq:1} can be reformulated in the language of discrete calculus as
\begin{equation}
\label{eq:4}
\lVert f - d_0(w) \rVert,
\end{equation}
where the scalar components $f_{ij}$ of the $1$-cochain $f=f_{ij}e^{ij}$ encode the pairwise comparison scores, and the components $w_i$ of the $0$-cochain $w=w_ie^i$ represent the ratings.
The minimizer of~\eqref{eq:4} coincides with the solution of Eq.~\eqref{eq:3} for $k=1$.

In this setting, the set of $0$-simplices $K_0$ corresponds to the teams $V$, the set of $1$-simplices $K_1$ to the comparisons $E$, and the set of $2$-simplices $K_2$ to the closed triples of comparisons:
\[
K_2 = \bigl\{ \{i,j,k\} : \{i,j\},\{j,k\},\{i,k\}\in E \bigr\}.
\]
For $k>2$, $K_k=\emptyset$.

@@

The dataset covers five soccer leagues: England, France, Germany, Italy and Spain.
Each league consists of $N=20$ teams, except for Germany, which has $N=18$.

in the major European soccer leagues (e.g., Premier League, La Liga, Serie A, Bundesliga, Ligue 1), the final standings are determined by a points system based on the results of matches during the season.
In the standard system, a win adds 3 points, a draw 1 point and a loss 0 points.
Each team plays every other team in the league twice (home and away) in what is called a round-robin format. 
Over the course of the season, the $i$-th team accumulates a total of $\pi_i$ points.
At the end of the season, the teams are ranked in descending order of total points.
If two or more teams have the same number of points, tiebreakers are applied. The exact rules vary slightly by league, but usually the order is something like:
Goal difference (GD): goals scored minus goals conceded.
Goals scored (GF): total number of goals scored during the season.
Head-to-head record: results of the matches between the tied teams (some leagues use this before GD).
Playoff or extra match: in rare cases (e.g., for the title, relegation, or European qualification) if all other criteria fail.
So the final standing (the ranking table at the end of the season) is determined by total points, with tiebreakers applied as needed.

@@

For each pair $\{i,j\}$ of teams in a given league, several pairwise metrics $m_{ij}$ and $m_{ji}$ are provided.
Each metric $m_{ij}$ takes a positive value when it presumably favors the home team $i$ over away team $j$, and takes a negative value otherwise.
The different types of empirically determined metrics being considered are:
\begin{enumerate}
\item {\bf crossings:}
\item {\bf counterattacks:}
\item {\bf pressure loss:}
\item {\bf build-up time:}
\item {\bf direct play:}
\item {\bf pressure points:}
\item {\bf shots:}
\item {\bf flow rate:}
\item {\bf maintenance time:}
\item {\bf middle-zone time:} bla bla.
\end{enumerate}
Moreover, the Singular Value Decomposition of previous emprically determined metrics are considered in order to define the so-called {\em styles} which are also some kind of metric~\cite{chacoma2025data}.

@@

With each metric, the coefficients
$$
f_{ij}
=
\frac{1}{2}(m_{ij}+m_{ji})
=
- f_{ji}
$$
are defined for each $i$ and $j$ such that $i<j$.
Moreover, in order to test the HodgeRank inference method, two types of ground-truth coefficients are also defined.
Namely, the rank-based coefficients $f_{ij}=i-j$ and the tournament points based coefficients $f_{ij}=\pi_j-\pi_i$.
In all cases there is an underlying fully connected network or graph with $N$ nodes, that is promoted to a simplicial complex composed of 0-simplices labeled by $i$, 1-simplices labeled by $ij$ with $i<j$ and 2-simplices labeled by $ijk$ with $i<j<k$.
Correspondingly, the coefficients $f_{ij}$ are promoted to be the components of a 1-cochain  $f$, where the anti-symmetric relation $f_{ji}=-f_{ij}$ must hold by definition.
